mixchar

### 2018-08-12 README.Rmd
remove build_vignettes line that may be causing pandoc error

Below we will show a basic implementation of the package. For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html). You can also find a full worked example either on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html) or in the vignette that you can access via R by installing with the `build_vignettes` argument as follows:

```{r, eval = FALSE}
devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
browseVignettes('mixchar')
```

>>>>

Below we will show a basic implementation of the package. For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html). You can also find a full worked example on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html).
